\section*{Acknowledgements}
\label{cheers}
After finishing this Final Year Project (FYP), I feel the need to look back and thank all the people that have helped and supported me during all this time. 

First I must thank my family, and specially my parents. For their attempt to understand endless nights (sometimes literally) confined with my computer to finish projects, assignments and deliveries. They will never cease to impress me with their infinite patience and unconditional support. Either with calls or in person, which has been a bit difficult lately, they have been always there to give me a pat on the back and say "You can do it". I must apologise with my parents, who came explicitly to Ireland to see me and I could not be all the time I wanted with them because of this project, and my own errors. I love you all and I thank you for the opportunity you gave me with my degree and this Erasmus.

To J.J. Collins, my supervisor and Erasmus coordinator in the University of Limerick. He has helped and guided me throughout all this project. Besides, he accepted my request of doing this FYP here, when I know it is not usual to do it abroad and it could have meant more work for him. For letting me know that "Working like a dog" is the only way things like this FYP are actually possible.

To all my classmates of the UC3M in general, and to my crazy group of friends in particular. For those talks before the exam to revise everything, from where I always learn something that was going to be in the exam, for those talks after to argue about "No, but I answered...", for those days and nights in the laboratories doing assignments. But also for laughing of everything, every time and no matter what, for making the University much easier just by being there. I thank you Luis, Jose and Juan for these four years. I want to thank Juan specially, for his direct support with this FYP, helping me to find the old notes from the second and third year (who could know they were going to be useful again), coming late to his swimming lessons because we were talking on Skype. \\
\\
To all the UC3M professors, because your passion for teaching inspired me and made me love this degree and the Carlos III University itself. Despite all the projects, exams and submissions that I once hated, I know I will miss these last 4 years.

To all the friends from my home town, Perales de Tajuña, and surroundings. You took me out of my house when an assignment was too hard, too long, too difficult. You just invited me to watch a movie, to talk about anything, to play some video games. Coming back home, the assignment suddenly was not that difficult, that long, that hard. It even seemed like it could be done. Thanks for being always there to get me a smile and, knowing it or not, for helping me in the process.

And last but not least, to the new friends I have made in my Erasmus in Ireland. When we came here 9 months looked like a lot of time, but now we are at the end of this experience and I cannot say any other thing than thanks. Being away from home has been difficult, but it would have been unbearable without friends. Thanks specially to my roomate Gautier, for the pizza nights, for the Gravity Falls episodes we watched every time we needed a break and for being a great friend that I will not forget.

Thanks to you all. 